A standard for the scholarly citation of archaeological data as an incentive to data sharing

### 2017-11-27 analysis/paper/paper.Rmd
add citation of dataset plot

# which provider is most cited?
library(urltools)

@@

# what sources do the most citing?

>>>>

# which provider is most cited?
# what sources do the most citing?

library(urltools)

@@

# look at the top ones, manually look them up
top_doi_providers <- 
events_df %>% 
  group_by(doi_provider) %>% 
  tally(sort= TRUE) %>% 
  filter(n >= 10)

top_doi_consumers <- 
events_df %>% 
  group_by(doi_consumer) %>% 
  tally(sort= TRUE) %>% 
  filter(n >= 10)

doi_lookup <- 
tribble(  ~doi,       ~doi_name,
 "10.5281",   "Zenodo",
 "10.5284",   "Medieval Archaeology",
 "10.6067",   "tDAR",
 "10.15468",  "GBIF",
 "10.14279",  "Technische Universität Berlin",
 "10.17026",  "EASY-DANS",
 "10.11141",  "Internet Archaeology",
 "10.1080",   "Various journal publishers") # OUP, CUP, Sage, Wiley, Springer

# join names to main table
events_df_names <- 
  events_df %>% 
  left_join(doi_lookup, by = c("doi_provider" = "doi")) %>% 
  rename(doi_provider_name = doi_name) %>% 
  left_join(doi_lookup, by = c("doi_consumer" = "doi"))  %>% 
  rename(doi_consumer_name = doi_name) %>% 
  mutate(base_url_consumer = suffix_extract(base_url_consumer)$domain) %>% 
  mutate(doi_consumer_name = if_else(is.na(doi_consumer_name), 
                                     base_url_consumer, 
                                     doi_consumer_name))

# cross-tab
events_df_names_ct <- 
events_df_names %>% 
  group_by(doi_provider_name, 
           doi_consumer_name) %>% 
  tally() %>% 
  filter(!is.na(doi_provider_name)) %>% 
  filter(!is.na(doi_consumer_name)) %>% 
  spread(doi_consumer_name, n, fill = 0)

library(wesanderson)
plot_citation_table <-
events_df_names %>% 
  group_by(doi_provider_name, 
           doi_consumer_name) %>% 
  tally() %>% 
  filter(!is.na(doi_provider_name)) %>% 
  filter(!is.na(doi_consumer_name)) %>% 
  ggplot(
         aes(str_wrap(str_trunc(doi_provider_name, side = "right", 35), 15),
             str_wrap(str_trunc(doi_consumer_name, side = "right", 35), 15))) +
  geom_point(aes(size = n),
             colour =  wes_palette("Rushmore")[1],
             shape = 16) +
  theme_bw() +
  xlab("Source") +
  ylab("Cited by") +
  scale_size_continuous(range=c(5,25)) +
  geom_text(aes(label = prettyNum(n, big.mark = ","))) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

ggsave("../figures/doi_citation_table.png",
       plot_citation_table,
       height = 7)
